Exploring TTC Delays

### 2024-01-24 outputs/paper/paper.qmd
submitted something for peer review. but at least the analysis from here will be easy.

```{r}
#| message: false
#| echo: false
#| label: tbl-cleaned_data
#| tbl-cap: Sample of Cleaned Delay Data

cleaned_transit_data <- read_csv(here::here("/outputs/data/cleaned_dataset.csv"))

head (cleaned_homicide_data, 5) 
```

@@

>>>>

@@

```{r}
#| message: false
#| echo: false
#| label: tbl-cleaned_data
#| tbl-cap: Sample of Cleaned Delay Data
#| fig-align: center

cleaned_transit_data <- read_csv(here::here("outputs/data/cleaned_dataset.csv"))

sample_table <- head(cleaned_transit_data, 5)

knitr::kable(sample_table)
```
